On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-22 Manuscript/manuscript.tex
Two New References

\paragraph{Recentered Percentile CI}
\jy{Can we come up with a good name for the proposed method? Other people may cite this.} \mc{bias-centered? i'm not sure}
\jy{How about ``recentered percentile''? It has the same length as the
  percentile approach but is centered at the point estimate.} \mc{replaced "proposed
  method" with "recentered"}

@@

\jy{use a better topic sentence.}
One of the goals of this study was to provide practical recommendations for 
necessary sample sizes when using block bootstrap to estimate parameters of 
serially dependent data. When using Student's $t$ intervals and $\phi$ is unknown,
the results of this study suggest that an $n \geq 800$ may be necessary for common practice to
estimate simpler parameters like $\mu$ or $\sigma_x$. If $\phi$ is already
known, a lesser $n$ may be adequate to estimate these parameters. For lower
absolute values of $\phi$, a smaller $n$ is sufficient when estimating $\mu$
or $\sigma$. For negative values of $\phi$, coverage of $\mu$ is higher in
general. In fact, Student's $t$ seems to over-cover $\mu$ for $\phi = - 0.4$
when using smaller sample sizes, meaning that if $\phi$ is known to have a
very negative value, another CI may be required. However, in real world
applications, $\phi$ is more commonly found to be positive, so Student's $t$
should still be used if $\phi$ is unknown. Lastly, to estimate $\phi$,
$n \geq 100$ using the Student's $t$ method may be sufficient. Further
investigation may be necessary to see if there are other interval corrections
that fix the coverage deterioration problem for $\phi$.

This study could be used as a guide for applied statistics courses for students
to generally understand how large of a sample size is sufficient for block
bootstrap to be used versus other inference methods. For undergraduate or
graduate students, block bootstrap is not typically a part of curriculum, but
the results of this study can easily be used to demonstrate when it is
practical to use this method. This information could also prove to be useful
for research using block bootstrap estimation of time series in domains such
as econometrics. Future studies could investigate if there are types of block
bootstrap interval construction such as $ABC$ or bootstrap-t intervals, or
alternatives to block bootstrap such as AR-Sieve bootstrap that would more
\jy{Cite references for AR-sieve}
appropriately recover the parameters of a time series.

\eds{Check out this paper:
Peter Buhlmann. "Bootstraps for Time Series." Statist. Sci. 17(1) 52 - 72, 
May 2002 - the conclusions of this paper are interesting in their own right:
``Disadvantages of the [block bootstrap] method include the following.
The block bootstrap sample should not be viewed as
a reasonable sample mimicking the data-generating
process: it is not stationary and exhibits artifacts where
resampled blocks are linked together. This implies that
the plug-in rule for bootstrapping an estimator $\hat{\theta}$ is not
appropriate. A prevectorization of the data is highly
recommended, but the bootstrapped estimator and its
computing routine may then need to be redesigned. As
a general nonparametric scheme, the block bootstrap
may be outperformed in various niches of stationary
time series, for example, for linear time series (see Section 3) 
and for categorical processes (see Section 5).
Second-order accuracy for a confidence interval has
been justified with the approach of Studentizing and
BCa correction (in the case of noncategorical time series); 
the latter was found to yield marginal improvement in a 
simulated example (we did not consider the former). }

One could also investigate the $n$ needed to make inferences about other forms
of serially dependent data such as a moving average process.

>>>>

\paragraph{Recentered Percentile CI}
\jy{Can we come up with a good name for the proposed method? Other people may
 cite this.} \mc{bias-centered? i'm not sure}
\jy{How about ``recentered percentile''? It has the same length as the
  percentile approach but is centered at the point estimate.} \mc{replaced
  all instances of "proposed
  method" with "recentered"}

@@

\jy{use a better topic sentence.} \mc{addressed}
One of the goals of this study was to provide some practical recommendations for 
necessary sample sizes when using block bootstrap to estimate parameters of 
serially dependent data. When using Student's $t$ intervals and $\phi$ is unknown,
the results of this study suggest that an $n \geq 800$ may be necessary for common practice to
estimate simpler parameters like $\mu$ or $\sigma_x$. If $\phi$ is already
known, a lesser $n$ may be adequate to estimate these parameters. For lower
absolute values of $\phi$, a smaller $n$ is sufficient when estimating $\mu$
or $\sigma$. For negative values of $\phi$, coverage of $\mu$ is higher in
general. In fact, Student's $t$ seems to over-cover $\mu$ for $\phi = - 0.4$
when using smaller sample sizes, meaning that if $\phi$ is known to have a
very negative value, another CI may be required. However, in real world
applications, $\phi$ is more commonly found to be positive, so Student's $t$
should still be used if $\phi$ is unknown. Lastly, to estimate $\phi$,
$n \geq 100$ using the Student's $t$ method may be sufficient. Further
investigation may be necessary to see if there are other interval corrections
that fix the coverage deterioration problem for $\phi$.

This study could be used as a guide for applied statistics courses for students
to generally understand how large of a sample size is sufficient for block
bootstrap to be used versus other inference methods. For undergraduate or
graduate students, block bootstrap is not typically a part of curriculum, but
the results of this study can easily be used to demonstrate when it is
practical to use this method. This information could also prove to be useful
for research using block bootstrap estimation of time series in domains such
as econometrics. Future studies could investigate the $n$ needed to make
inferences about other forms
of serially dependent data such as a moving average process. One could also
investigate if there are types of block
bootstrap interval construction such as $ABC$ or bootstrap-t intervals, or
alternatives to block bootstrap, such as AR-Sieve bootstrap
 \citep{kreiss1992bootstrap}, that would more
\jy{Cite references for AR-sieve} \mc{addressed}
appropriately recover the parameters of a time series. In addition, as noted by
\citet{buhlmann2002bootstraps}, there are some 
general drawbacks of block bootstrap - with respect to how reasonably it imitates 
the data-generating process - which may be addressed in a future study.

\eds{Check out this paper:
Peter Buhlmann. "Bootstraps for Time Series." Statist. Sci. 17(1) 52 - 72, 
May 2002 - the conclusions of this paper are interesting in their own right:
``Disadvantages of the [block bootstrap] method include the following.
The block bootstrap sample should not be viewed as
a reasonable sample mimicking the data-generating
process: it is not stationary and exhibits artifacts where
resampled blocks are linked together. This implies that
the plug-in rule for bootstrapping an estimator $\hat{\theta}$ is not
appropriate. A prevectorization of the data is highly
recommended, but the bootstrapped estimator and its
computing routine may then need to be redesigned. As
a general nonparametric scheme, the block bootstrap
may be outperformed in various niches of stationary
time series, for example, for linear time series (see Section 3) 
and for categorical processes (see Section 5).
Second-order accuracy for a confidence interval has
been justified with the approach of Studentizing and
BCa correction (in the case of noncategorical time series); 
the latter was found to yield marginal improvement in a 
simulated example (we did not consider the former). } \mc{addressed}
